NEED TITLE

### 2015-06-18 ms.tex
moved section on velocity graph to after section on plots and numerical results

\section{Detailed Simulations of Turbulent Collapse}

@@

We have also implemented a new algorithm for mesh refinement in these simulations. As gas collapse under self gravity, certain regions rapidly increase in density. These regions are refined when the Truelove criterion ($\lambda \le 4 \Delta x$) is met. This corresponds to a condition on the density 
\begin{equation}
\frac{\rho}{\rho_{0}} = 45 \cdot 4^{l} \left( \frac{N_{root}}{128} \right)^2 \left( \frac{16 \text{pc}}{L} \right)^2 \left( \frac{c_{s}}{2.65\text{x}10^4 \text{cm s$^{-1}$}} \right)^2 \left( \frac{3 \text{x}10^{-22} \text{g cm$^{-3}$}}{\rho_{0}} \right)
\label{eq:refinement_criteria}
\end{equation}
 where $l$ is the refinement level, with $l = 0$ corresponding to the root grid. When this density condition is met the local grid is refined by a factor of 2 provided that the maximum refinement level has not reached. 
We reach a maximum of $\rho / \rho_{0} \approx 3 \text{x} 10^{7}$ at $l$ = 8, the maximum refinement level. Thus we traverse nearly 8 orders of magnitude in the density in our AMR simulations.
When the Truelove criterion is met at the highest refinement level, the excess mass in a cell is transferred either to a newly created sink particle or to a sink particle whose accretion radius includes the cell. This behavior is the same as in Lee et al. (2014), albeit at a much higher resolution. We should also note that like Lee et al. (2014), our sink particle creation prescription is different from the prescription of Federrath et al (???) where additional checks need to be performed.
Our base grid's resolution of $128^3$ gives a cell length of $1.2 \text{x} 10^{-1}$pc which is sufficient to resolve the Jean's length
\begin{equation}
\lambda_J \equiv \sqrt{\frac{\pi c_{s}^2}{G \bar{\rho}}} \approx 3.5 \text{pc}
\end{equation}

@@

At the instance in time shown in Figure \ref{fig:entire projection}, a total of 20 star particles have been formed. A couple of these star particles are formed in isolation though the majority formed in binaries and there is a ring of ten in one region. They congregated in several star forming regions shown in Figure \ref{fig:star forming regions}. In these regions, the sink particles that are formed lay within 0.1 pc of one another, which reflects that the highest density regions are concentrated toward the center. Visually, the character of accretion at the this outer scale appear to flow along filaments, though previous work (Lee et al. 2014) has shown that the majority of accretion is spherical. We discuss this more quantitatively below {\bf INCLUDE A STUDY OF LARGE SCALE ACCRETION}

\begin{figure*}
\plottwo{Disk_0132_0000.png}{Disk_0132_0002.png}
\caption{Cut of the two star forming regions.\label{fig:star forming regions}}
\end{figure*}

@@

@@

>>>>

\section{Detailed Simulations of Turbulent Collapse} \label{sec:simulation setup}

@@

We have also implemented a new algorithm for mesh refinement in these simulations. As gas collapse under self gravity, certain regions rapidly increase in density. These regions are refined when the Truelove criterion ($\lambda \le 4 \Delta x$) is met. This corresponds to a condition on the density 
\be
\frac{\rho}{\rho_{0}} = 45 \cdot 4^{l} \left( \frac{N_{root}}{128} \right)^2 \left( \frac{16 \text{pc}}{L} \right)^2 \left( \frac{c_{s}}{2.65\text{x}10^4 \text{cm s$^{-1}$}} \right)^2 \left( \frac{3 \text{x}10^{-22} \text{g cm$^{-3}$}}{\rho_{0}} \right)
\label{eq:refinement_criteria}
\ee
 where $l$ is the refinement level, with $l = 0$ corresponding to the root grid. When this density condition is met the local grid is refined by a factor of 2 provided that the maximum refinement level has not reached. 
We reach a maximum of $\rho / \rho_{0} \approx 3 \text{x} 10^{7}$ at $l$ = 8, the maximum refinement level. Thus we traverse nearly 8 orders of magnitude in the density in our AMR simulations.
When the Truelove criterion is met at the highest refinement level, the excess mass in a cell is transferred either to a newly created sink particle or to a sink particle whose accretion radius includes the cell. This behavior is the same as in Lee et al. (2014), albeit at a much higher resolution. We should also note that like Lee et al. (2014), our sink particle creation prescription is different from the prescription of Federrath et al (???) where additional checks need to be performed.
Our base grid's resolution of $128^3$ gives a cell length of $1.2 \text{x} 10^{-1}$pc which is sufficient to resolve the Jean's length
\be
\lambda_J \equiv \sqrt{\frac{\pi c_{s}^2}{G \bar{\rho}}} \approx 3.5 \text{pc}
\ee

@@

At the instance in time shown in Figure \ref{fig:entire projection}, a total of 20 {\bf GET ACCURATE COUNT} star particles have been formed. A couple of these star particles are formed in isolation though the majority formed in binaries and there is a ring of ten in one region. They congregated in several star forming regions shown in Figure \ref{fig:star forming regions}. In these regions, the sink particles that are formed lay within 0.1 pc of one another, which reflects that the highest density regions are concentrated toward the center. Visually, the character of accretion at the this outer scale appear to flow along filaments, though previous work (Lee et al. 2014) has shown that the majority of accretion is spherical. We discuss this more quantitatively below {\bf INCLUDE A STUDY OF LARGE SCALE ACCRETION}

\begin{figure*}
\plottwo{Disk_0132_0000.png}{movie_quad3_frame_0320_part_0000_05pc.png}
\caption{Cut of the two star forming regions. The region on the right formed a single isolated particle, after two filaments {\bf INCLUDE5PC image? } had collided.\label{fig:star forming regions}}
\end{figure*}

% Start with quad3 gold standard

The first particle formed in isolation and remained isolated for the remainder of the simulation run. It is $\approx 1.6x10^5\text{yrs}$ old and is $\approx 10 M_{\odot}$

%% Include image of the velocity and disk

@@

%\begin{figure*}
%\plottwo{movie_disk_0132_0001.png}{movie_disk_0132_0003.png}
%\plottwo{movie_disk_0132_0000.png}{Disk_0132_0000.png}
%\caption{The upper frames, and the bottom left frame show slices along the angular momentum axis of three local particles in one of the regions demonstrating significant star formation.  Each of the zoomed-in slices have a radius of $0.02$ pc.  To determine the angular momentum axis, we take a $0.01$ pc region about the densest local point and calculate the angular momentum vector.  We then take a slice in the plane normal to the angular momentum vector to plot the regions around these dense points.  The bottom right frame shows the zoomed-out region of formation, with a radius of $1.5$ pc.    \label{fig:snapshots}}
%\end{figure*}

@@

\subsection{Radial Profile of Velocity after Star Formation}

{\bf Include condition to place in which shell?}
We start with the isolated case seen in the right image of figure \ref{fig:star forming regions}. In Figure \ref{fig:quad3_320_velocity}, we show the radial distribution of $v_r$, $v_\phi$, $V_{kepler}$, $v_{turbulent}$ in spherical shells around the star particle. In calculating these values, we use a spherical geometry, though we're working on subtracting the velocity in a  cylindrical geometrical case as well. 
FLASH provides us with $\vec{v}$ in each cell, which includes the bulk flow of the cloud. To remove the bulk flow velocity we calculate the momentum of the material inside of (including) the thin spherical shell we're interested in. We then remove that mass weighted velocity from the total velocity. This give us our total velocity line in figure \ref{fig:quad3_320_velocity} (the magenta "dot" line). 
To obtain the radial infall velocity (blue triangle line) we used $p_r[i] = \vec{v_r}[i] \cdot \vec{r}[i] * m[i]$ equation \ref{eq:obtain_vr} to obtain the radial momentum of the ith cell inside the spherical shell of interest. We then sum over all $p_{r}[i]$ that are in the shell, divide by the total mass in the shell and obtain the mass weighted radial velocity for that shell. 
To obtain $\vec{v_{\phi}}$ we start with equation \ref{eq:calc v_phi} as we need to know the directionality of $\vec{v}_{\phi}$ in order to properly subtract it to obtain $v_{turbulent}$.

\be
\vec{v}_{\phi} = \vec{\Omega} \times \vec{r}
\label{eq:calc v_phi}
\ee
With \ref{eq:calc v_phi} in mind, we start with what we know from FLASH, $\vec{r}$ and $\vec{v}$ for each cell, and use that to obtain $\vec{L}$

\be
\vec{L}_{shell} = \sum{\vec{r} \times \vec{v} * m}
\label{eq:calc L shell}
\ee
where the sum is over all cells in the shell and $\vec{L_{shell}}$ is the angular momentum vector of the shell. We also calculate the elements of the moment of Inertia tensor for each cell.

\be
I_{ii} = (x_{jj}^2 + x_{kk}^2) * m[n]
I_{ij} = -x_{i}[n]*x_{j}[n] * m[n]
\label{eq:moment of inertia}
\ee
for the nth cell in the shell. We sum over all cells in the shell to obtain the Inertia tensor for each shell.
We use $\vec{L}$ and $I$ to obtain $\Omega$

\be
I^{-1}\vec{L} = \Omega
\label{eq:Obtain Omega}
\ee
having obtained $\Omega$ we refer back to \ref{eq:calc v_phi} and plot the results in figure \ref{fig:quad3_320_velocity} where the black +'s are $v_{\phi}$.

In calculating the turbulent velocity we used a slightly more intelligent approach then the brute force subtract in quadrature.
\be
\vec{v}_{t} = \sqrt{\vec{v}^2 + \vec{v}_{\phi}^2 + \vec{v}_{r}^2 - 2(\vec{v} \cdot \vec{v}_{\phi}) - 2(\vec{v} \cdot \vec{v}_{r}) + 2(\vec{v}_{\phi} \cdot \vec{v}_{r})}
\label{eq:Vrms subtraction}
\ee

as a check that we were accounting for all of the velocity that we started with, we did a quick check using $\vec{v}_{sum} = \sqrt{\vec{v}^2 + \vec{v}_{\phi}^2 + \vec{v}_{r}^2 + \vec{v}_{t}}$ and it traces $\vec{v}$ extremely well.

The dashed red line is the Keplerian velocity:
\be
\vec{v}_{K} = \sqrt{G m \over \vec{r}}
\label{eq:Kepler velocity}
\ee

The authors want to touch upon the fact that the total velocity ($\vec{v}$) does not quite match up with $\vec{v}_{K}$. The reason is, as one can see from the plotted line of $c_s$ in figure (\ref{fig:quad3_320_velocity}) the flows are mostly super or trans-sonic. Thus, one should expect to see shocks, which would remove some energy from the flow in the form of thermal heating. These simulations, as mentioned in section \ref{sec:simulation setup} are isothermal. Thus, the heating that results from these shocks is immediately radiated away.

%\begin{equation}
%p_r[i] = \vec{v_r}[i] \cdot \vec{r}[i] * m[i]
%vr_nomass[i] = (vx[i]*x[i] + vy[i]*y[i] + vz[i]*z[i])/r[i]
%vr = vr_nomass[i] * cellMass[i]%
%
%\label{eq:obtain_vr}
%\end{equation}

\begin{figure}
\plotone{velocity_quad3_0320_shellsphere_000.pdf}
\caption{Plot of the run of velocities for the isolated star particle seen in the right image of figure \ref{fig:star forming regions}. The dotted line in magenta is the numerical total velocity. The dot-dash green line is the turbulent velocity, the blue triangle line is the radial infall while the black $+$ is $v_{\phi}$. A color version of this plot is available online.
\label{fig:quad3_320_velocity}}
\end{figure}
